\section{Series}

\subsection{Definition}
\udef Let $(V, \norm)$ be a normed vector space.\\
Let $a : \N \to V$. Let $K \in \N$.\\
We say that a series
\[
    \sum_{n=K}^{\infty} a_n
\]
is \emph{convergent} if the associated \emph{sequence of partial sums}
$S_K : \N \to V$ converges.
The term $S_K^n$ is, for $n \in \N$, defined as
\[
    S_K^n := \sum_{k=K}^{n} a_k
\]
If $K = 0$, we usually write $S^n$ or $S_n$ instead of $S_0^n$.
If the series $\sum_{n=K}^{\infty}$ is convergent, the \emph{value} of the series
is defined as the limit of the sequence of partial sums, i.e.
\[
    \sum_{k=K}^{\infty} a_k := \lim_{n \to \infty} S_K^n
        = \lim_{n \to \infty} \sum_{k=K}^{n} a_k.
\]

\subsection{Geometric series}
\uprop Let $a \neq 1$ and $n \in \N$. Then
\[
    \sum_{k=0}^{n} a^k = \frac{1 - a^{n+1}}{1 - a}.
\]

\subsubsection*{}
\uprop Let $a \in (-1, 1)$. Then
\[
    \sum_{k=0}^{\infty} a^k = \frac{1}{1-a}.
\]

\subsection{Harmonic Series}
\uprop The series
\[
    \sum_{k=1}^{\infty} \frac{1}{k}
\]
diverges.

\subsection{Hyperharmonic Series}
\uprop Let $p > q$ then the series
\[
    \sum_{k=1}^{\infty} \frac{1}{k^p}
\]
converges.

\subsubsection*{Basel Problem}
\uthm
\[
    \sum_{n=1}^{\infty} \frac{1}{n^2} = \frac{\pi^2}{6}
\]


\subsection{Only the tail matters for convergence}
\uprop Let $(V, \norm)$ be a normed vector space.\\
Let $a : \N \to V$. Let $K,L \in \N$. Then the series
\[
    \sum_{n=K}^{\infty} a_n
\]
converges if, and only if,
\[
    \sum_{n=L}^{\infty} a_n
\]
converges. Moreover, if they converge and $K < L$, then
\[
    \sum_{n=K}^{\infty} a_n = \sum_{n=K}^{L-1} a_n + \sum_{n=K}^{\infty} a_n.
\]

\subsubsection*{}
\uprop Let $(V, \norm)$ be a normed vector space.\\
Let $a : \N \to V$. Let $M \in \N$. Assume the series
\[
    \sum_{k=M}^{\infty} a_k
\]
is convergent. Then
\[
    \lim_{m \to \infty} \sum_{k=m}^{\infty} a_k = 0.
\]

\subsubsection*{Index shift for sequences}
Let $(V, \norm)$ be a normed vector space.\\
Let $a : \N \to V$, let $M, l \in \N$. Then the series
\[
    \sum_{k=M}^{\infty} a_k
\]
converges if, and only if,
\[
    \sum_{k=M}^{\infty} a_{k+l}
\]
converges. Moreover, if they converge,
\[
    \sum_{k=M}^{\infty} a_{k+l} = \sum_{k=M+l}^{\infty} a_k.
\]


\subsection{Divergence test}
\uthm Let $(V, \norm)$ be a normed vector space.\\
Let $a : \N \to V$. Suppose the series $\sum_{n=0}^{\infty} a_n$ converges.
Then
\[
    \lim_{n \to \infty} a_n = 0.
\]
In other words: if the limit $\lim_{n \to \infty} a_n$ diverges or is not
equal to $0$, then the series $\sum_{n=0}^{\infty} a_n$ diverges.\\
\warning This condition is necessary but \emph{not} sufficient.


\subsection{Limit laws for series}
\uthm Let $(V, \norm)$ be a normed vector space.\\
Let $a,b : \N \to V$. Let $\lambda \in \R$.\\
Suppose $\sum_{k=0}^{\infty} a_k$ and $\sum_{k=0}^{\infty} b_k$ converge.\\
Then the following series converge and are equal to,
\begin{enumerate}[(i)]
    \item $\sum_{k=0}^{\infty} (a_k + b_k) = \sum_{k=0}^{\infty} a_k + \sum_{k=0}^{\infty} a_k$,
    \item $\sum_{k=0}^{\infty} (\lambda a_k) = \lambda \sum_{k=0}^{\infty} a_k$.
\end{enumerate}